# Updated Schedule {- #schedule}

I will keep this page with the updated schedule for the semester. You can find these readings on Canvas.

**Class meets Tuesdays and Thursdays, 2:30–3:45 pm.**

**Quizzes.** There is a short quiz at the **start of class every Thursday** (5 minutes), run through **iClicker** on your phone, tablet, or laptop. The quiz opens when class starts and closes a few minutes later. There is no quiz on Thursdays when we do not meet (09/24, 10/08, and Thanksgiving 11/26), and none on the first day (08/20) — 12 quizzes in total. Your **two lowest quiz scores are dropped**.

**iClicker.** We use iClicker every class meeting, for the Thursday quizzes and for short in-class polls on the material that count toward participation. It is **free for all UTSA students**. Set up your account and add this course before our second class (08/25) — see the syllabus for step-by-step instructions.

**Note on the final exam.** The final is on **Thursday, December 10, from 1:00 to 2:50 pm** — this is *not* our usual class time. The time and room are set by the UTSA registrar and cannot be moved.

```{r, echo=FALSE, include=FALSE}
title_line <- "| Week| Session | Topic| Required reading| Method| Deliverable | \n"
separation_line <- "| -- | -- | -- | -- | -- | -- | \n"
create_session <- function(vector) {
  week <- vector[1]
  session <- vector[2]
  topic <- vector[3]
  reading <- vector[4]
  method <- vector[5]
  deliverable <- vector[6]

  paste0(c("|", week, "|", session, "|", topic, "|", reading, "|", method, "|", deliverable, "|", "\n"))
}
# Fall 2026 Schedule - Classes on Tuesday and Thursday at 2:30-3:45 pm
# First day of classes: Wed 08/19 (our first meeting is Thu 08/20)
# No class: Tue 09/01, Thu 09/24, Thu 10/08, Thu 11/26 (Thanksgiving)
# Midterm: Tue 10/06. Last class: Thu 12/03. Final: Thu 12/10, 1:00-2:50 pm

s_intro <- c(
  "1: 08/20", # date
  "1", # session
  "Introduction to the course", # topic with link
  " ", # reading
  " ", # method
  " "
) # deliverable

s_geomob <- c(
  "2: 08/25", # date
  "2", # session
  "[Geography of Upward Mobility in America](#lec1_geomobility)", # topic with link
  "[Chetty, Friedman, Hendren, Jones and Porter (2018)-<br>**Non-technical summary**](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306202) ", # reading
  "Correlation, regression", # method
  " "
) # deliverable

s_introR <- c(
  "2: 08/27", # date
  "3", # session
  "[Intro to R and data](#getting-started)", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 1** (start of class)"
) # deliverable

s_noclass_sep1 <- c(
  "3: 09/01", # date
  "-", # session
  "**No Class**", # topic with link
  " ", # reading
  " ", # method
  " "
) # deliverable

s_introR2 <- c(
  "3: 09/03", # date
  "4", # session
  "Intro to [Visualization](#viz), [Wrangling](#wrangling) and [RMarkdown](#rmarkdown)", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 2** (start of class)<br>First short report (In class) - [Project 0](#project0)"
) # deliverable

s_causaleffects <- c(
  "4: 09/08", # date
  "5", # session
  "[Intro to Causal Effects of Neighborhoods](#lec2_causaleffect) ", # topic with link
  "[Bergman, Chetty, DeLuca, Hendren, Katz and Palmer (2019) -<br>Non-technical summary](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306205) ", # reading
  "Experiments (RCTs)", # method
  ""
) # deliverable

s_causaleffects2 <- c(
  "4: 09/10", # date
  "6", # session
  "[Characteristics of High-Mobility Areas](#lec2_causaleffect) and [Correlation Analysis](#regression) ", # topic with link
  "[Bergman, Chetty, DeLuca, Hendren, Katz and Palmer (2019) -<br>Introduction](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306208) ", # reading
  "Quasi-experiments ", # method
  "**Quiz 3** (start of class)<br>[Project 1](#project1) – Part 1 (for Saturday 09/12)"
) # deliverable

s_mto <- c(
  "5: 09/15", # date
  "7", # session
  "[Moving to Opportunity and place based policies](#lec3_mto-placebased) ", # topic with link
  " ", # reading
  "Cost-benefit analysis ", # method
  ""
) # deliverable

s_mob_hist_int <- c(
  "5: 09/17", # date
  "8", # session
  "[Historical and International Evidence on](#lec4_mob-hist-int) and [Drivers of Inequality and Mobility](#lec4_mob-hist-int) ", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 4** (start of class)<br>[Project 1](#project1) – Part 1 and 2 (for Saturday 09/19)"
) # deliverable

s_hist_int_cont <- c(
  "6: 09/22", # date
  "9", # session
  "Continuation of Historical and International Drivers of Mobility ", # topic with link
  " ", # reading
  " ", # method
  ""
) # deliverable

s_noclass_sep24 <- c(
  "6: 09/24", # date
  "-", # session
  "**No Class** (no quiz)", # topic with link
  " ", # reading
  " ", # method
  " "
) # deliverable

s_catchup <- c(
  "7: 09/29", # date
  "10", # session
  "Catch-up session and project work in class ", # topic with link
  " ", # reading
  " ", # method
  ""
) # deliverable

s_review_mid <- c(
  "7: 10/01", # date
  "11", # session
  "Review for Midterm ", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 5** (start of class)"
) # deliverable

s_mid <- c(
  "8: 10/06", # date
  "-", # session
  "**Midterm** (in class) ", # topic with link
  " ", # reading
  " ", # method
  ""
) # deliverable

s_noclass_oct8 <- c(
  "8: 10/08", # date
  "-", # session
  "**No Class** (no quiz)", # topic with link
  " ", # reading
  " ", # method
  " "
) # deliverable

s_midsolution <- c(
  "9: 10/13", # date
  "12", # session
  "Midterm solution, and Project 2 work in class ", # topic with link
  " ", # reading
  " ", # method
  ""
) # deliverable

s_mob_ed <- c(
  "9: 10/15", # date
  "13", # session
  "[Higher Education and Upward Mobility](#lec5_mob-ed) ", # topic with link
  "[Dynarski, Libassi, Michelmore and Owen (2018)](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306212)", # reading
  "Regression discontinuity ", # method
  "**Quiz 6** (start of class)"
) # deliverable

s_recap_quarto <- c(
  "10: 10/20", # date
  "14", # session
  "Recap of R and Quarto Documents ", # topic with link
  " ", # reading
  " ", # method
  "[Project 2](#project2) (for Thursday 10/22) "
) # deliverable

s_ed_higher <- c(
  "10: 10/22", # date
  "15", # session
  "[Causal Effects of Higher Education](#lec6_ed-higher) ", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 7** (start of class)"
) # deliverable

s_k12 <- c(
  "11: 10/27", # date
  "16", # session
  "[Primary education](#lec7_k12)", # topic with link
  "[Chetty, Friedman and Rockoff (2011)-<br>Non-technical summary](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306213)	", # reading
  "Experiments ", # method
  " "
) # deliverable

s_teachers <- c(
  "11: 10/29", # date
  "17", # session
  "[Teachers and Charter Schools](#lec8_teachers-charters)", # topic with link
  "	", # reading
  "Event study designs, competitive equilibrium ", # method
  "**Quiz 8** (start of class)"
) # deliverable

s_racedis <- c(
  "12: 11/03", # date
  "18", # session
  "[Racial Disparities in Economic Opportunity](#lec9_race-ineq) ", # topic with link
  "[Bertrand, and Mullainathan (2004)](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306215)	", # reading
  "Dynamic models and steady states ", # method
  " "
) # deliverable

s_jud_sys <- c(
  "12: 11/05", # date
  "19", # session
  "[Improving judicial decisions](#lec10_criminal-justice)", # topic with link
  "[Kleinberg, Lakkaraju, Leskovec, Ludwig and Mullainathan (2017)](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306220) ", # reading
  "Machine learning, implicit bias ", # method
  "**Quiz 9** (start of class)"
) # deliverable

s_immigration <- c(
  "13: 11/10", # date
  "20", # session
  "Immigration ", # topic with link
  "[Tabellini (2020)](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306223)  ", # reading
  "Instrumental variables ", # method
  ""
) # deliverable

s_ml <- c(
  "13: 11/12", # date
  "21", # session
  "Implementing a simple machine learning model in R - Part 1", # topic with link
  "  ", # reading
  "  ", # method
  "**Quiz 10** (start of class)"
) # deliverable

s_ml2 <- c(
  "14: 11/17", # date
  "22", # session
  "Implementing a simple machine learning model in R - Part 2", # topic with link
  "  ", # reading
  "  ", # method
  "[Project 3](#project3) (for Thursday 11/19)"
) # deliverable

s_polecon <- c(
  "14: 11/19", # date
  "23", # session
  "Political Economy ", # topic with link
  "  ", # reading
  " ", # method
  "**Quiz 11** (start of class)"
) # deliverable

s_tax <- c(
  "15: 11/24", # date
  "24", # session
  "Income taxation ", # topic with link
  "[Diamond and Saez (2011)](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306227)  ", # reading
  "Supply and demand; synthetic control ", # method
  " "
) # deliverable

s_thanksgiving <- c(
  "15: 11/26", # date
  "-", # session
  "**Thanksgiving – No Class** (no quiz)", # topic with link
  " ", # reading
  " ", # method
  " "
) # deliverable

s_pollution <- c(
  "16: 12/01", # date
  "25", # session
  "Intro to air and water pollution, and externalities ", # topic with link
  "[Isen, Rossin-Slater, and Walker (2017)-<br>Non-technical summary](https://utsa.instructure.com/courses/79928/files/folder/papers?preview=13306233)", # reading
  "Difference in difference ", # method
  "[Project 4](#project4) - (for Thursday 12/03)"
) # deliverable

s_review_final <- c(
  "16: 12/03", # date
  "26", # session
  "Review session — **last day of class** ", # topic with link
  " ", # reading
  " ", # method
  "**Quiz 12** (start of class)"
) # deliverable

s_final <- c(
  "Finals: 12/10", # date
  "-", # session
  "**Final Exam, 1:00–2:50 pm** (note: not our usual class time) ", # topic with link
  " ", # reading
  " ", # method
  ""
) # deliverable
```

```{r tableSchedule, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- paste0(c(
  title_line,
  separation_line,
  create_session(s_intro),
  create_session(s_geomob),
  create_session(s_introR),
  create_session(s_noclass_sep1),
  create_session(s_introR2),
  create_session(s_causaleffects),
  create_session(s_causaleffects2),
  create_session(s_mto),
  create_session(s_mob_hist_int),
  create_session(s_hist_int_cont),
  create_session(s_noclass_sep24),
  create_session(s_catchup),
  create_session(s_review_mid),
  create_session(s_mid),
  create_session(s_noclass_oct8),
  create_session(s_midsolution),
  create_session(s_mob_ed),
  create_session(s_recap_quarto),
  create_session(s_ed_higher),
  create_session(s_k12),
  create_session(s_teachers),
  create_session(s_racedis),
  create_session(s_jud_sys),
  create_session(s_immigration),
  create_session(s_ml),
  create_session(s_ml2),
  create_session(s_polecon),
  create_session(s_tax),
  create_session(s_thanksgiving),
  create_session(s_pollution),
  create_session(s_review_final),
  create_session(s_final)
))
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```
